The globular cluster system of the Auriga simulations

### 2020-04-09 response_to_referee.tex

\section*{Comments for each section}
\subsection*{Introduction}
\begin{itemize}
\item Item
\end{itemize}

\subsection*{Sect. 2 -}
\begin{itemize}
\item We added the halo mass range of the Auriga simulations.
\item The last paragraph should now make more sense after updating the introduction.
\end{itemize}

\subsection*{Sect. 3 -}
\begin{itemize}
\item We added references to section 3.3, 3.4, and 3.5 in the first paragraph of section 3.
\item Section 3.2 has been restructured.
\item We removed the standard error on the mean and replaced `dispersion' 
by `standard deviation' in section 3.3.
\item We added a sentence to clarify the last statement in section 3.4.
\end{itemize}

\subsection*{Sect. 4 -}
\begin{itemize}
\item We added the mean number of GC candidates compared to the mean number of
star particles in the Auriga L4 galaxies. In addition, Figure 3 now shows the 
number of star particles included in the subset.
\item We clarified at various places whether we mean the mean or median among
the simulations, or if we refer to the absolute value of one of the galaxies.
\item We added the suggestion in the 3rd paragraph of section 4.1.
\item Bimodality in GC systems is now discussed in the introduction.
\item Figure 4 - now has a vertical line to indicate the metallicity cut 
between metal-poor and metal-rich GC subpopulations in the Milky Way.
\item We added a sentence about the cluster formation efficiency model of 
Kruijssen (2012) in the last paragraph of section 4.1.
\item We now show the median instead of the mean for the galactocentric radius in
section 4.2 and Figure 6.
\item Figure 6: no changes were made for rescaling the galaxies (i.e. we still
use the virial radius)
\item Figure 5 and 7: shaded regions now show the 25-75th percentiles.
\item We added a brief discussion of Figure 8.
\item We clarified that we are referring to Figure 5 and Figure 7 for the claims about
the {\it in situ} and accreted component in the third paragraph of section 4.3.
\item Figure 9: The values are removed from the masked upper right corner bins.
\item Figure 2,8,9: The values of the upper and right axes have been removed from
Figure 2 and 9 (observations) for clarity (rather than the suggestion to add 
axis labels and units). However, we did not mask these bins for Figure 8 (Auriga)
because it illustrates our finding that the simulations produce a considerable
amount of mass in GC candidates with low metallicities at large radii.
\end{itemize}

### 2020-04-09 AurigaGCS.tex
Done with Section 4

@@

We find that the age cut, on average, lowers the mean metallicity $<$[Fe/H]$>$ from 
$0.0$ to $-0.6$. Furthermore, accreted GC candidates generally have lower mean 
metallicities than the {\it in~situ} subset with differences of roughly
${\sim}0.3$~dex for the majority of the simulation runs. This behaviour can be 
seen in \mbox{Au4-21}, while a slightly larger difference of ${\sim}0.5$~dex is 
seen for \mbox{Au4-10} (as plotted), \mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} 
and \mbox{Au4-22}. However, this trend is reversed for \mbox{Au4-1} and \mbox{Au4-4} 
for which the {\it in~situ} subset has a lower mean metallicity instead. 
\mbox{Au4-1} is undergoing a major merger at redshift zero and we find a mean
metallicity in this simulations $\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} 
(accreted) GC candidates, although the former consists of only $1019$ particles 
($1.3$\% of all GC 
candidates, and with a total mass of $5 \times 10^{7}$~M\Sun). For \mbox{Au4-4}, 
only ${10.8}$\% of the GC candidates is classified as {\it in~situ} (compared to 
{\it in~situ} fractions of ${40-80}$\% for other haloes). We note that \mbox{Au4-4}
has undergone a major merger around 2~Gyr lookback time, which is probably why
the accreted population is more metal rich. After inspection of the same figure 
for every one of the $30$~Auriga L4 haloes we find that the simulations produce
(sub)populations of GC candidates that are more metal-rich than the MW and M31 GCSs.
Moreover, none of the simulations produces GC candidates with a bimodal metallicity 
distribution.

@@

We show the ratio of the  simulated to the observed profiles in the middle and bottom
panels. This mass excess can be thought of the `mass budget' that the Auriga GC 
candidates can `afford to lose' due to a combination of smaller than unity bound
cluster formation efficiencies combined with a Hubble time of dynamical evolution,
while still producing sufficient mass at the right metallicities. In particular,
the cluster formation efficiency would have to decrease with decreasing 
metallicity for Auriga GC candidates to produce a population of GC candidates 
that is consistent with the MW. For the GC candidates in M31 we find a constant 
mass ratio up to [Fe/H]=$-0.9$, above which the simulations produce a higher mass ratio 
with increasing metallicity. If dynamical evolution is not expected to more 
efficiently disrupt GCs of higher metallicity, then we would find that the 
efficiency to form bound star clusters would have to decrease with increasing 
metallicity.

@@

We investigate whether the Auriga simulations still produce sufficient mass when
the GC candidates are two-dimensionally binned in [Fe/H] and $r_\text{gal}$. First
we sum the total mass of GC candidates in each bin (for an individual Auriga 
simulation), then we calculate the median total mass in each bin over all 
$30$~Auriga L4 haloes. The result is shown in Figure~\ref{fig:Au-FeHRgc}, which 
can be compared to the observed total GC mass shown in 
Figure~\ref{fig:observations_FeHRgc}.

@@

We now focus on four quadrants of this diagram, split at [Fe/H]~=~-1 (metal-poor 
or metal-rich) and $r_\text{gal}$~=~8~kpc (inside or outside the Solar radius).
The majority of the mass in Auriga GC candidates is produced in metal-rich star
particles inside the Solar radius. The total mass is dominated by the {\it in situ} 
component, for [Fe/H] as well as for $r_\text{gal}$. The total mass excess in 
this region increases with decreasing metallicity for the MW and M31, and there
is a weak trend of decreasing over-production with increasing radius for the
{\it in situ} subsets but no trend with radius for the accreted GC candidates.
As for the metal-rich GC candidates outside the Solar radius, we find that the
mass excess with respect to the median is largest in this corner for the MW and
M31. The main reason for this trend are the lower GC counts in the observations,
whereas the Auriga simulations efficiently form metal-rich GC candidates and
have no problem to produce them at large radii. The opposite is true for the
metal-poor GC candidates inside the Solar radius, where the mass surplus with
respect to the median is smallest for both galaxies. However, the disruption rates
are expected to be particularly high for GCs in the inner regions of galaxies
that are on orbits with pericentres close to the galactic bulge or bar. In addition, 
disk crossings in this region will cause spikes in the tidal tensor due to steep
density gradients that could be highly disruptive to the GCs. The bins with the 
lowest `mass budget' are in this region (a factor 9 for the MW and 22 for M31).
The bound cluster formation efficiency has to exceed 10\%, and none of the GC 
candidates in this region can experience significant mass loss in order for Auriga
to produce sufficient mass in this quadrant. Finally, the metal-poor GC candidates
outside the Solar radius have lower than average mass ratios, which is not 
surprising given that the Auriga simulations overall underproduce low-metallicity
stars particles.

>>>>

TODO: ``\citet{2012MNRAS.426.1475U} shows the great variety in GC metallicity distributions
present in the sample of early-type galaxies of the SLUGGS survey contradicts
the classical idea that all the metallicity distributions of GCs should be bimodal.''

@@

We find that the age cut, on average, lowers the mean metallicity $<$[Fe/H]$>$ from 
$0.0$ to $-0.6$. This reflects the enrichment history of the galaxy because the
age cut neglects the more metal-rich stellar population which shifts the mean
metallicity towards lower values. Furthermore, accreted GC candidates generally have
lower mean metallicities than the {\it in~situ} subset with differences of roughly
${\sim}0.3$~dex for the majority of the simulation runs. This behaviour can be 
seen in \mbox{Au4-21}, while a slightly larger difference of ${\sim}0.5$~dex is 
seen for \mbox{Au4-10} (as plotted), \mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} 
and \mbox{Au4-22}. However, this trend is reversed for \mbox{Au4-1} and \mbox{Au4-4} 
for which the {\it in~situ} subset has a lower mean metallicity instead. 
\mbox{Au4-1} is undergoing a major merger at redshift zero and we find a mean
metallicity in this simulations $\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} 
(accreted) GC candidates, although the former consists of only $1019$ particles 
($1.3$\% of all GC 
candidates, and with a total mass of $5 \times 10^{7}$~M\Sun). For \mbox{Au4-4}, 
only ${10.8}$\% of the GC candidates is classified as {\it in~situ} (compared to 
{\it in~situ} fractions of ${40-80}$\% for other haloes). We note that \mbox{Au4-4}
has undergone a major merger around 2~Gyr lookback time, which is probably why
the accreted population is more metal rich. After inspection of the same figure 
for every one of the $30$~Auriga L4 haloes we find that the simulations produce
(sub)populations of GC candidates that are more metal-rich than the MW and M31 GCSs.
Moreover, none of the simulations produces GC candidates with a bimodal metallicity 
distribution.

@@

We show the ratio of the  simulated to the observed profiles in the middle and bottom
panels. This mass excess can be thought of the `mass budget' that the Auriga GC 
candidates can `afford to lose' due to a combination of smaller than unity bound
cluster formation efficiencies combined with a Hubble time of dynamical evolution,
while still producing sufficient mass at the right metallicities. In particular,
the cluster formation efficiency would have to decrease with decreasing 
metallicity for Auriga GC candidates to produce a population of GC candidates 
that is consistent with the MW. For the GC candidates in M31 we find a constant 
mass ratio up to [Fe/H]=$-0.9$, above which the simulations produce a higher mass ratio 
with increasing metallicity. If dynamical evolution is not expected to more 
efficiently disrupt GCs of higher metallicity, then we would find that the 
efficiency to form bound star clusters would have to decrease with increasing 
metallicity. This trend could be consistent with the cluster formation efficiency 
model of \citet{2012MNRAS.426.3008K} as lower metallicity star particles formed 
at earlier times when the bound cluster formation efficiencies are higher due
to higher pressure birth environments.

@@

We investigate whether the Auriga simulations still produce sufficient mass when
the GC candidates are two-dimensionally binned in [Fe/H] and $r_\text{gal}$. First
we sum the total mass of GC candidates in each bin (for an individual Auriga 
simulation), then we calculate the median total mass in each bin over all 
$30$~Auriga L4 haloes. The result is shown in Figure~\ref{fig:Au-FeHRgc}, which 
can be compared to the observed total GC mass shown in 
Figure~\ref{fig:observations_FeHRgc}. We notice that the simulations produce
relatively little mass in metal-poor GC candidates at small radii and in metal-rich
GC candidates at large radii. However, there is still few times $10^7$ M$_{\odot}$
produced by the simulations in the uppermost 3 bins where no observed GCs are found.

@@

We now focus on four quadrants of this diagram, split at [Fe/H]~=~-1 (metal-poor 
or metal-rich) and $r_\text{gal}$~=~8~kpc (inside or outside the Solar radius).
The majority of the mass in Auriga GC candidates is produced in metal-rich star
particles inside the Solar radius. The total mass is dominated by the {\it in situ} 
component, for [Fe/H] as well as for $r_\text{gal}$ as can be seen in Figure~\ref{fig:FeH}
and Figure~\ref{fig:Rgc}. The total mass excess in 
this region increases with decreasing metallicity for the MW and M31, and there
is a weak trend of decreasing over-production with increasing radius for the
{\it in situ} subsets but no trend with radius for the accreted GC candidates.
As for the metal-rich GC candidates outside the Solar radius, we find that the
mass excess with respect to the median is largest in this corner for the MW and
M31. The main reason for this trend are the lower GC counts in the observations,
whereas the Auriga simulations efficiently form metal-rich GC candidates and
have no problem to produce them at large radii. The opposite is true for the
metal-poor GC candidates inside the Solar radius, where the mass surplus with
respect to the median is smallest for both galaxies. However, the disruption rates
are expected to be particularly high for GCs in the inner regions of galaxies
that are on orbits with pericentres close to the galactic bulge or bar. In addition, 
disk crossings in this region will cause spikes in the tidal tensor due to steep
density gradients that could be highly disruptive to the GCs. The bins with the 
lowest `mass budget' are in this region (a factor 9 for the MW and 22 for M31).
The bound cluster formation efficiency has to exceed 10\%, and none of the GC 
candidates in this region can experience significant mass loss in order for Auriga
to produce sufficient mass in this quadrant. Finally, the metal-poor GC candidates
outside the Solar radius have lower than average mass ratios, which is not 
surprising given that the Auriga simulations overall underproduce low-metallicity
stars particles.
